The five axes of the Turtle: symmetry and asymmetry in NGC~6210

### 2020-12-07 ms.tex
Update to timescale figure (now Fig 22)

\begin{figure}
  \includegraphics[width=\linewidth]
  {figs/turtle-flow-axis-history}
  \caption{
    Ejection history of each flow axis,
    assuming no acceleration or deceleration of the features.
    Lower-case roman numerals indicate sub-axes of axis~E.
    Uncertainties are typically of order \(\pm 30\%\),
    see Table~\ref{tab:3d} for details,
    except for \AxP{E}(ii) where the uncertainty is much higher.
  }
  \label{fig:axis-history}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]
  {figs/turtle-flow-axis-history}
  \caption{
    Ejection history of each flow axis,
    assuming no acceleration or deceleration of the features.
    Lower-case roman numerals indicate sub-axes of axis~E.
    Uncertainties are typically of order \(\pm 30\%\),
    see Table~\ref{tab:3d} for details,
    but are larger for \AxM{D} and \AxM{E}(ii).
    For Axis~E, semi-circular symbols indicate lower limits,
    while fainter symbols show the results of a re-analysis
    assuming a worst-case systematic uncertainty in the proper motions.
  }
  \label{fig:axis-history}
\end{figure}
